%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Authors:
% Ali Afzal
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} 
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Ali Afzal}}}} % First name
	
	\vspace{6pt}
	
	{\Large Student $\sim$ ELTE} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
    \icon{User}{11}{06-12-2002}\\
    \icon{Phone}{11}{+36 706 495284}\\
    \icon{MapMarker}{11}{Budapest, Hungary}\\
    
	
\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\icon{Envelope}{11}{\href{mailto:afzal.ali.alld@gmail.com}{afzal.ali.alld@gmail.com}}\\	
    \icon{Github}{11}{\href{https://github.com/afzalaman}{github.com/afzalaman}}\\
    \icon{LinkedinSquare}{11}{\href{https://www.linkedin.com/in/afzal-ali-elte/}{/in/afzal-ali-elte}}\\    
    
\end{minipage}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.46\textwidth}
    \cvsect{Summary}
	\vspace{-6pt}
 
    %Dummy text
	I am currently a BSc student at Eötvös Loránd University with a keen interest in Software Engineering. I am also working as an OOP Demonstrator at the University. I am passionate about new technologies and always open to acquiring new knowledge
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.465\textwidth}
    \cvsect{Skills}
    \vspace{-6pt}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Languages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
      Java, C/C++, C sharp, SQL, Swift, VBA, Python, JavaScript, HTML, PHP, GoLang, Haskell.  
    \end{minipage}
    \vspace{4mm}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Other:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
    .Net, Apache Jmeter, REST API, Unity Engine, Good knowledge of Algorithms and Data Structures.
    \end{minipage}
    
\end{minipage}


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
    \entry
		{2021 - 2025}
		{BSc Computer Science }
		{Eötvös Loránd University, Budapest - HU}
		{Ongoing, Bachelor's Degree on Stipendium Hungaricum Scholarship}
  
  \entry
		{2016 - 2020}
		{High School Diploma}
		{CISCE, New Delhi - IN}
		{GPA of 3.39 out of 4}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Experience}
\begin{entrylist}
	\entry
        {8/2023 -- 2/2024}
		{Reporting Team - Intern}
		{Vodafone Intelligent Solutions - VOIS, Budapest - HU}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Utilizing VBA in Excel to automate and enhance monthly and quarterly executive reports for senior leadership decision-making.
            \item Leading the transition from traditional Excel reports to a modern online dashboard format using Qlik Sense technology, ensuring seamless integration and data visualization.
        \end{itemize} 
        % \texttt{SQL} \slashsep \texttt{Excel}
        }
	\entry
        {2/2023 -- 7/2024}
		{OOP Course Demonstrator}
		{Eötvös Loránd University, Budapest - HU}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Object Oriented Programming Lab Instructor
            \item Facilitating teaching responsibilities for Professor by designing and assessing challenging tasks, exams, and coursework in OOP course. Conducting student consultations, addressing inquiries, and explaining OOP concepts to enhance learning experiences.
        \end{itemize} 
        % \texttt{SQL} \slashsep \texttt{Excel}
        }
	
\end{entrylist}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
	\cvsect{Languages}
    \vspace{-6pt}
    
    \hspace{26mm} \textbf{English} - C1, \textbf{ Hungarian} - A1, \textbf{ Hindi} - native, \textbf{ Urdu} - native

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
    \entry
		{JAVA}
		{Capitaly Simulation Game}
		{\href{https://github.com/afzalaman/Capitaly-Simulation-Game}{github.com}}
		{%Dummy text 
        Simulation of a simplified Capitaly game, implementing diverse player strategies, property transactions, and chance events, with parameters read from a text file, allowing for efficient testing and providing detailed game outcomes, including the winning player's financial status and owned properties.}
    \entry
		{Rest API}
		{Rest Mobile Phone}
		{\href{https://github.com/afzalaman/rest-mobile-phone}
        {github.com}}
		{%Dummy text 
        REST-based application which can store and present information about mobile phones created using the FastAPI framework in Python. It uses Uvicorn server}
	\entry
		{C}
		{Vineyard-Simulation}
        {\href{https://github.com/afzalaman/Vineyard-Simulation}
        {github.com}}
		{A vineyard simulation application for efficient spring season worker management. Utilized inter-process communication techniques, including pipes and message queues, to coordinate worker transportation and provide real-time status updates. Demonstrated expertise in process management and signal handling in a Unix-like environment.}
    \entry
		{PHP}
		{Polling Web Application}
        {\href{https://github.com/afzalaman/Polling-Web-Application}
        {github.com}}
		{A web application where logged-in users can create or cast their votes on polls (questionnaires/forms)}
    \entry
		{Concurrency}
		{Pigs Simulation}
        {\href{https://github.com/afzalaman/pigs-simulation}
        {github.com}}
		{Designed and implemented a multi-threaded simulation in Java. Demonstrated expertise in concurrent programming and simulation design.}
	\entry
		{JavaScript}
		{Light the Bulb Game}
		{\href{https://github.com/afzalaman/Light-the-bulb-Game}
        {github.com}}
		{A grid game developed using JavaScript}
    \entry
		{C++}
		{Atmospheric Gases}
		{\href{https://github.com/afzalaman/Atmospheric-Gases}
        {github.com}}
		{Implemented a concise C++ program using design patterns to simulate atmospheric layer transformations influenced by changing conditions. Demonstrated proficiency in C++, Design Patterns, and File I/O.}
    \entry
		{JAVA}
		{Labyrinth Game}
		{\href{https://github.com/afzalaman/Labyrinth-Game}
        {github.com}}
		{Created a Java Labyrinth game with JDBC integration for database connectivity and Java Swing for the GUI. Implemented dynamic gameplay with a moving dragon, tracked player statistics in a database, and provided features for displaying high scores.}
    \entry
		{JAVA}
		{Hunting Game}
		{\href{https://github.com/afzalaman/Hunting-Game}
        {github.com}}
		{Developed a two-player Hunting Board Game with Java Swing GUI. Players strategically move characters on an adjustable board to either capture or escape.}
    \entry
		{Concurrency}
		{Field Race Simulation}
		{\href{https://github.com/afzalaman/FieldRace}
        {github.com}}
		{Java program for a concurrent field race simulation with players and checkpoints. Implemented thread synchronization using ExecutorService, AtomicBoolean, and ConcurrentHashMap. Achieved dynamic scoring, periodic display, and program termination.}
    \entry
		{DSA}
		{Custom Data types implementations}
		{\href{https://github.com/afzalaman/DataTypes-Implemetation}
        {github.com}}
		{Different datatypes implementation in C++}
    \entry
		{HTML/CSS}
		{Home2Decor Website}
		{\href{https://github.com/afzalaman/Mini-Website}
        {github.com}}
		{A small interior designer company website using HTML/CSS and Bootstrap 5}
  
\end{entrylist}


\end{document}
